---
title: "Adding Rows to a panelsummary Table"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding Rows to a panelsummary Table}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.height = 4
)
```

```{js, echo = F}
$( document ).ready(function() {
  $(".lightable-classic").removeClass("table").css("display", "table");
});
```

This vignette shows how to add rows to `panelsummary` tables. Since `panelsummary::panelsummary` returns `kableExtra` objects, adding rows is impossible using the base function `panelsummary::panelsummary`. This can be a nuisance when you want to include additional statistics to your table. However, the workaround is to use the `panelsummary::panelsummary_raw` function. 

## panelsummary::panelsummary_raw

The `panelsummary::panelsummary_raw` function returns a dataframe that can be  manipulated. The trade-off is that the table will need to be customized using the `kableExtra` package, although some of this customization can be completed using the `panelsummary::clean_raw` function (see example).

## Workflow

If you want to create a table with panels that has additional statistical rows, the workflow will be the following:

* Estimate your models (preferably with the `fixest` package).
* Pass your models into `panelsummary::panelsummary_raw` to get a manipulable dataframe.
* Manipulate the dataframe (preferably with `dplyr::add_row`).
* Use `panelsummary::clean_raw` to return a `kableExtra` object.
* Use `kableExtra::pack_rows` to create panel labels.


## Example: Adding Additional Rows to Each Panel 

To demonstrate how to add a row to each panel of a `panelsummary::panelsummary_raw` table, I will assume that each panel needs one additional row for the wild-cluster-bootstrap p-values of the `cyl` column from the `mtcars` data. While I will not explicitly calculate these (in fact, they will be completely made up), the following steps will show how to complete such task.  

Consider the following models, estimated using the `fixest` package:

```{r setup}
library(panelsummary)

## Panel A: mpg dependent variable
mpg_1 <- fixest::feols(mpg ~cyl + disp, data = mtcars)
mpg_2 <- fixest::feols(mpg ~ cyl + am, data = mtcars)

## Panel B: wt dependent variable
wt_1 <- fixest::feols(wt ~ cyl + disp, data = mtcars)
wt_2 <- fixest::feols(wt ~ cyl + am, data = mtcars)

```

Recall that putting each of these two models in a list will result in multiple specifications per-panel.

```{r}
## putting each panel's models into a list—one for each panel
panel_a_mpg <- list(mpg_1, mpg_2)
panel_b_wt <- list(wt_1, wt_2)
```

Now, I will pass these two lists into `panelsummary::panelsummary_raw`. Note that this function shares many of the same arguments as `panelsummary::panelsummary`. In the following, I will also use the arguments `stars` (significance stars), `mean_dependent` (for dependent variable mean), and `gof_omit` (to omit $R^2$ statistics):

```{r}
## creating the dataframe
panelsummary_raw(panel_a_mpg, panel_b_wt,
                 stars = "econ",
                 mean_dependent = T,
                 gof_omit = "^R")
```

The return value of this output is a dataframe without panel labels. Given that it is a dataframe, you can use `dplyr` functions to easily manipulate. For instance, I will use the `dplyr::add_rows` function to add the pseudo wild-cluster-bootstrap p-values to the table:

```{r}
## adding rows using dplyr::add_row
bootstrap_table <- panelsummary_raw(panel_a_mpg, panel_b_wt,
                 stars = "econ",
                 mean_dependent = T,
                 gof_omit = "^R") |> 
  dplyr::add_row(term = "Wild Cluster Boot P-value (cyl)",
                 `Model 1` = ".001",
                 `Model 2` = ".002",
                .before = 10) |> 
  dplyr::add_row(term = "Wild Cluster Boot P-value (cyl)",
                 `Model 1` = ".001",
                 `Model 2` = ".005",
                 .before = 22)

bootstrap_table
```

Now the dataframe is ready to be passed into `kableExtra::kbl` to further customize it with panel headers/columnnames etc. Alternatively, you can use the `panelsummary::clean_raw` function to get a few desirable traits and speed up the process. In particular, the  `panelsummary::clean_raw` function does the following by default:

* Passes the dataframe into `kableExtra::kbl` 
* Changes the alignment to Left for the first column, and Center for all remaining columns.
* Changes the names of the columns to a blank white space for the first column, and consecutive numbers in the remaining columns.

However, you can also pass in a caption using the `caption` argument:

```{r}
## creating a kableExtra object with a few desirable defaults
bootstrap_table |> 
  clean_raw(caption = "A customized panelsummary table with added rows.")
```

Finally, to get the desired panel labels, you will need to use `kableExtra::pack_rows`:

```{r}
## creating the final panels.
bootstrap_table |> 
  clean_raw(caption = "A customized panelsummary table with added rows.") |> 
  kableExtra::pack_rows("Panel A: MPG", 1, 12,
                        italic = T,
                        bold = F) |> 
  kableExtra::pack_rows("Panel B: Cyl", 13, 24, 
                        italic = T,
                        bold = F) |> 
  kableExtra::footnote(list("* p < 0.1, ** p < 0.05, *** p < 0.01")) |> 
  kableExtra::kable_classic(full_width = F, html_font = "Cambria") 
```

