---
title: "Introduction to panelsummary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to panelsummary}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`panelsummary` consists of one main function, `panelsummary::panelsummary`, to provide a simple, yet customizable way to create a regression table with multiple panels. As of this writing, the package is intended for use with regressions of class `lm` and `fixest`, with an emphasis on the latter. There are more classes in the pipeline, and you can always check `panelsummary::models_supported` for an exhaustive list of models supported. 

To begin, load in the `panelsummary` package.

```{r setup}
library(panelsummary)
```


## Motivating Example

To motivate the power of `panelsummary`, consider a model using the `mtcars` dataset:

$$ Y_{i} = hp_i + cyl_i + e_i$$
Where $Y_i$ is the dependent variable, which can be either $mpg_i$ or $disp$ of car $i$, $hp_i$ is the horsepower, $cyl_i$ is the number of cylinders, and $e_i$ is the error term. To estimate this model with both of the dependent variables, the following code is provided:

```{r}
## estimating the model with two depedent variables:
## 1) mpg and 2) disp
mpg_1 <- lm(mpg ~ hp + cyl, data = mtcars)
disp_1 <- lm(disp ~ hp + cyl, data = mtcars)
```

While one option to present the regression coefficients in a table would be to create a separate regression table for each, there is a more concise, and cleaner way to present this information. This is where `panelsummary` is most useful. With a simple pass of `panelsummary::panelsummary`, a beautiful regression table is created without any additional editing, and can immediately be viewed in the RStudio Viewer panel. 

```{r}
## creating a beautiful regression table with panelsummary
panelsummary(mpg_1, disp_1, 
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"))
```

Note that the number of arguments passed into `...` is how the delineation of panels is determined. Importantly, the length of the character vector passed into `panel_labels` must match the number of arguments passed into `...`. This ensures that each panel has its own label. 

## Cleaning Variable Names

Behind the scenes, `panelsummary` uses `modelsummary` to help create the regression tables. The benefit of this is the ability to use `coef_map` argument (which is passed through to `modelsummary::modelsummary`) to clean variable names. Recall that to use `coef_map`, the syntax is `c("old_name" = "new_name")`:

```{r}
panelsummary(mpg_1, disp_1, 
             coef_map = c("hp" = "Horse Power",
                          "cyl" = "Cylinder"),
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"))
```

For more information on `coef_map`, see the [modelsummary website](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#coef-renameomitmap).

## Excluding Goodness-of-Fit Statistics

Similar to cleaning names, `panelsummary` also supports the `gof_map` and `gof_omit` arguments from `modelsummary`. In the following, `gof_map` will be used to change the name of "Num.Obs" to "Observations" and "F" to "F-stat", while removing the other goodness-of-fit statistics:


```{r}
## mapping the goodness of fit statistics to new names - see modelsummary for more details
gm <- tibble::tribble(
        ~raw,      ~clean,          ~fmt,  ~omit,
        "nobs",      "Observations",     0,  FALSE,
        "F", "F-stat",               3,  FALSE
)
panelsummary(mpg_1, disp_1, 
             coef_map = c("hp" = "Horse Power",
                          "cyl" = "Cylinder"),
             gof_map = gm,
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"))
```

For more information on how to use `gof_map`, see the [modelsummary website](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#gof_map).

## Adding Additional Models to the Table

It is simple to add additional models to each panel in the table. This is most useful when presenting robustness of estimates with a variety of different explanatory variables. As an example, consider three more models with `mpg` as the dependent variable:

```{r}
## creating two additional models for the first panel 
mpg_2 <- lm(mpg ~ hp + cyl + drat, data = mtcars)
mpg_3 <- lm(mpg ~hp + cyl + drat + wt, data = mtcars)
```

To add these models to Panel A, simply replace `mpg_1` with `list(mpg_1, mpg_2, mpg_3)` in the original code:

```{r}
panelsummary(list(mpg_1, mpg_2, mpg_3), disp_1, 
             coef_map = c("hp" = "Horse Power",
                          "cyl" = "Cylinder",
                          "drat" = "Rear Axle Ratio",
                          "wt" = "Weight (1000lbs)"),
             gof_map = gm,
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"))
```

## Adding Additional Panels to the Table

As alluded to, the number of arguments passed into `...` will determine the number of panels created in the table. Hence, simply add another argument to `...`, and a corresponding label to `panel_labels`:

```{r}
panelsummary(list(mpg_1, mpg_2, mpg_3), disp_1, list(mpg_1, mpg_2),
             coef_map = c("hp" = "Horse Power",
                          "cyl" = "Cylinder",
                          "drat" = "Rear Axle Ratio",
                          "wt" = "Weight (1000lbs)"),
             gof_map = gm,
             panel_labels = c("Panel A: MPG", "Panel B: Displacement", "Panel C: Demonstration of Additional Panel"))
```



At this time, `panelsummary` **will only support up to five panels**. This is done intentionally to discourage an overly long table. 

## Adding Significance-Stars

To add significance stars, simply set the `stars` argument to `TRUE`. By default, `panelsummary` uses the following convention (symbol=pvalue): +=.1, \*=.05, \*\*=.01, \*\*\*=0.001.

To change the significance, a character vector can be passed in with custom values:

```{r}
## change the significance stars to match economic convention
table_stars <- panelsummary(list(mpg_1, mpg_2, mpg_3), disp_1, 
             coef_map = c("hp" = "Horse Power",
                          "cyl" = "Cylinder",
                          "drat" = "Rear Axle Ratio",
                          "wt" = "Weight (1000lbs)"),
             gof_map = gm,
             stars =c('*' = .1, '**' = .05, '***' = .01),
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"))
table_stars 
```

## Customizing With `kableExtra`

When `panelsummary::panelsummary` is executed, a `kableExtra` object is created. The benefit of this feature is that all of `kableExtra`'s customizing functions are ready to pipe into. For instance, suppose a header above the model numbers, a footnote denoting significance:
```{r}
library(kableExtra)

table_stars |> 
  kable_classic() |> 
  add_header_above(c(" " = 1, "Models Using mtcars" = 3)) |> 
  footnote(list("* p < 0.1, ** p < 0.05, *** p < 0.01",
                "Customizations done using kableExtra package"))
```

