---
title: "Using panelsummary with fixest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using panelsummary with fixest}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette focuses on using the `panelsummary` package with the `fixest` package. `fixest` has become one of the most popular regression packages for economists, and therefore further capabilities have been implemented in `panelsummary` to work seemlessly with `fixest`. There will be two main capabilities that this vignette covers:

1. Adding the mean of the dependent variable.
2. Collapsing fixed effects.

## Adding the Mean of the Dependent Variable

To start, load in the `fixest`, `panelsummary`, and `kableExtra` packages. 

```{r setup}
library(panelsummary)
library(fixest) ## for regressions
library(kableExtra) ## for further table customization
```

For demonstration purposes, four regressions are estimated with the `fixest` package using the `feols` function and the `mtcars` data:

```{r}
## estimating two models for mpg
mpg_1 <- mtcars |>
    feols(mpg ~  cyl | gear + carb, cluster = ~hp)

mpg_2 <- mtcars |>
    feols(mpg ~  cyl | gear + carb + am, cluster = ~hp)


## estimating the same two models for disp
disp_1 <- mtcars |> 
  feols(disp ~ cyl | gear + carb, cluster = ~hp)

disp_2 <- mtcars |> 
  feols(disp ~ cyl | gear + carb + am, cluster = ~hp)
```

To create a regression table with two panels (Panel A: MPG/Panel B: Displacement) and two models in each, the lists `list(mpg_1, mpg_2)` and `list(disp_1, disp_2)` can be passed into the arguments for `...`. However, since each of these models is of the class `fixest` (i.e., created with the `fixest` package), the `mean_dependent` argument can be set to `TRUE` to show the means of the dependent variable in each column:

```{r}
panelsummary(list(mpg_1, mpg_2), list(disp_1, disp_2), 
             mean_dependent = TRUE,
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"),
             caption = "Automated Mean of Dependent Variable") |> 
  kable_classic()
```

Notice that a new row was placed before the "Num.Obs." row in each panel with the mean of the dependent variable. Note that the placement of the mean can be reordered with the `gof_map` argument. For instance, suppose the desired table consists only of number of observations, the mean of dependent variable, and fixed effects, in that respective order. A new tibble can be created (see the [modelsummary website](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#gof_map)) to map/rename these goodness-of-fit statistics into the correct order. **Observe that the mean of the dependent variable's raw name is `mean`, and in this case, is being renamed to `Mean(DV)`.**

```{r}
## creating a renaming tibble to pass into panelsummary 
gm <- tibble::tribble(
        ~raw,      ~clean,          ~fmt,  ~omit,
        "nobs", "Observations", 0,  FALSE,
        "mean", "Mean(DV)", 3, FALSE,
        "FE: gear", "FE: Gear", 0, FALSE,
        "FE: carb", "FE: Carb", 0, FALSE,
        "FE: am", "FE: AM", 0, FALSE,
        "F", "F-stat", 3,  FALSE
)

## creating the regression table
panelsummary(list(mpg_1, mpg_2), list(disp_1, disp_2),
             mean_dependent = TRUE,
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"),
             gof_map = gm,
             caption = "Automated Mean of Dependent Variable-Renamed and Reordered") |> 
  kable_classic() |> 
  footnote("'mean' is the raw name when mapping")

```

## Collapsing Fixed Effects

Notice that in the tables above that the fixed effects in columns (1) and (2) are the same across each panel. To reduce the number of rows, the `collapse_fe` argument can be used to show a separate panel containing only the fixed effects:

```{r}
panelsummary(list(mpg_1, mpg_2), list(disp_1, disp_2),
             mean_dependent = TRUE,
             panel_labels = c("Panel A: MPG", "Panel B: Displacement"),
             gof_map = gm,
             caption = "Collapsed Fixed Effects",
             collapse_fe = T) |> 
  kable_classic() |> 
  footnote("Collapsing the fixed effects assumes the fixed effects in all panels are the same!")
```

Although it does not appear in HTML, a LaTeX version of this table will include a horizontal line separating the fixed effects from the other panels. This can be switched off using the `hline_before_fe` argument. 
